lnc34a splice junctions

### 2017-12-01 inst/lnc34a_cage/lnc34a_cage.Rmd
updating rmds according to fileMap

```{r}
nrCellLinesDown <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master"
  url <- fileMap(type = "txt")["suppFigure3d"][[1]]
  read_tsv(gzcon(url(file.path(dataUrl, url)))) %>% 
    pull(cell) %>%
    unique() %>%
    length()
}

cellLinesInFinal <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure3d"][[1]]
  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    pull(cell) %>%
    unique()
}

RNAprepTable <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure3d"][[1]]
  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    mutate(`rna extract` = str_replace(`rna extract`, "total", "total RNA")) %>%
    select(`rna extract`) %>%
    count(`rna extract`)
}

localizationTable <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure3d"][[1]]
  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    select(localization) %>%
    count(localization)
}

@@

#cage data
url <- fileMap(type = "rds")["suppFigure3d"][[1]]
cage <- read_rds(gzcon(url(file.path(dataUrl, url))))

>>>>

```{r}
nrCellLinesDown <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master"
  url <- fileMap(type = "txt")["suppFigure4a"][[1]]
  read_tsv(gzcon(url(file.path(dataUrl, url)))) %>% 
    pull(cell) %>%
    unique() %>%
    length()
}

cellLinesInFinal <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure4a"][[1]]
  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    pull(cell) %>%
    unique()
}

RNAprepTable <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure4a"][[1]]
  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    mutate(`rna extract` = str_replace(`rna extract`, "total", "total RNA")) %>%
    select(`rna extract`) %>%
    count(`rna extract`)
}

localizationTable <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure4a"][[1]]
  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    select(localization) %>%
    count(localization)
}

@@

#cage data
url <- fileMap(type = "rds")["suppFigure4a"][[1]]
cage <- read_rds(gzcon(url(file.path(dataUrl, url))))

### 2017-12-01 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
updating rmds according to fileMap

```{r}
nrCellLinesDown <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "txt")["suppFigure3e"][[1]]

@@

cellLinesInFinal <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure3e"][[1]]

@@

RNAprepTable <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure3e"][[1]]
  final <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    select(filename) %>%
    distinct() %>%
    mutate(filename = str_replace(filename, "^(.*)\\.bedRnaElements.*", "\\1"))

  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "txt")["suppFigure3e"][[1]]
  read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
    filter(X__15 %in% pull(final, filename)) %>%
    rename(`rna extract` = X__3) %>%
    select(`rna extract`) %>%
    count(`rna extract`)
}
```

@@

#splice junctions
url <- fileMap(type = "rds")["suppFigure3e"][[1]]
splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))

>>>>

```{r}
nrCellLinesDown <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "txt")["suppFigure4b"][[1]]

@@

cellLinesInFinal <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure4b"][[1]]

@@

RNAprepTable <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure4b"][[1]]
  final <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    select(filename) %>%
    distinct() %>%
    mutate(filename = str_replace(filename, "^(.*)\\.bedRnaElements.*", "\\1"))

  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "txt")["suppFigure4b"][[1]]
  read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
    filter(X__15 %in% pull(final, filename)) %>%
    rename(`rna extract` = X__3) %>%
    select(`rna extract`) %>%
    count(`rna extract`)
}
```

@@

#splice junctions
url <- fileMap(type = "rds")["suppFigure4b"][[1]]
splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))
